New orbits of irregular satellites for the predictions of stellar occultations up to 2020

### 2016-06-27 Irregular-occ/Irregular-occ.tex
.

\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites based on thousands of new observations and predictions for stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,\newauthor
R. Vieira-Martins$^{1,2,5,\dag}$,
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$Institut de m\'ecanique c\'eleste et de calcul des \'eph\'em\'erides - Observatoire de Paris, UMR 8028 du CNRS, 77 Av. Denfert-Rochereau,\\ 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

\begin{abstract}
%Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size, shape, albedo and composition, to trace back their true origin. The best ground-based technique to determine size and shape, and thus constrain the albedo and in a broader sense composition, is the observation of stellar occultations by these objects but this demands a very precise ephemeris based on new and good positions.
%\cite{GomesJunior2015} published 6523 observations obtained between 1992 and 2014 for 18 irregular satellites with an estimated error in the positions of about 60 to 80 mas.
%Based on this observations, we aimed to generate new numerical integration of the orbits of eight largest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda. This is a short-time ephemeris that corrected systematic errors from previous ephemeris (JPL JUP300). For Phoebe we updated ephemeris from \cite{Desmars2013} using 75\% more positions than the previous one.
%Also Jupiter will cross the galactic plane in 2019-2020 and Saturn in 2018. This creates a good opportunity to predict stellar occultations due to the large number of events that can be predicted in these periods. Thus, we aimed to predict stellar occultations for the same 9 satellites cited above. Using the UCAC4 catalogue we managed to identify \noccs candidates of stellar occultations between the period of January, 2016 and December, 2020.
%We discuss how the successful observation of a stellar occultation by these objects is quite possible and present some of those potential occultations.
\cite{GomesJunior2015} published 6523 positions for 18 irregular satellites from observations made between 1992 and 2014 with an estimated error of about 60 to 80 mas. Based on this set of positions, we performed numerical integrations for deriving new orbits for the eight largest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda. This corrected systematic errors and resulted in an ephemeris more accurate/precise than JPL jup300 for these bodies at least in the immediate future. For Phoebe we updated the ephemeris from \cite{Desmars2013} using 75\% more positions than the previous one. Due to their orbital characteristics, it is common belief that the irregular satellites were captured by the giant planets in the early Solar System, but there is no consensus for a single model explaining where they were formed. Size, shape, albedo and composition would help to trace back their true origin, but these physical parameters are yet poorly known for irregular satellites. The observation of stellar occultations would allow for the determination of such parameters. Indeed Jupiter will cross the galactic plane in 2019-2020 and Saturn in 2018, improving a lot the chances of observing such events in the near future. Using the derived ephemerides and the UCAC4 catalogue we managed to identify \noccs candidate stellar occultations between January 2016 and December 2020 for the 9 satellites studied here. We discussed how the successful observation of a stellar occultation by these objects is possible and present some potential occultations.
\end{abstract}

@@

\citetalias{GomesJunior2015} published 6523 precise positions for 18 irregular satellites from observations made at the Observatório do Pico dos Dias (OPD), Observatoire Haute-Provence (OHP) and European Southern Observatory (ESO) between 1992 and 2014.

@@

The obtained ephemeris is hereafter refered as STE, for Special-Tailored Ephemeris. The initial osculating elements at the origin of integration are presented in Table \ref{Tab: sat_ell}.

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0 with respect to the center of Jupiter.
 }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & I$\degr$ & $\Omega\degr$ & $\omega\degr$ & $v\degr$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular} 
\end{center}
\begin{flushleft}
\textbf{Notes}: a: semimajor axis; e : excentricity; I: inclination relative to the equatorial reference plane J2000; $\Omega$: longitude of the ascending node; $\omega$: argument of periapsis; $v$: true anomaly.
\end{flushleft}
\end{table*}

@@

Fig. \ref{Fig: JPL-STE} displays the offsets of the positions published by \citetalias{GomesJunior2015} for the satellite Carme in declination relative to the STE ephemeris, to \cite{Jacobson2012} jup300 JPL ephemeris and \cite{Emelyanov2008} ephemeris.We see that the systematic JPL ephemeris offsets pointed out by \citetalias{GomesJunior2015} are reduced with our ephemeris, as expected.

\begin{figure}
\includegraphics[width=8.8cm]{figures/Carme_ephemeris.eps}
\caption{Offsets in declination of the positions published by \protect\citetalias{GomesJunior2015} for Carme. The red "x" relative to the special-tailored ephemeris, the blue "+" relative to the jup300 JPL ephemeris and the green dot relative to \protect\cite{Emelyanov2008}. As expected, the ephemeris systematic errors pointed out by \protect\citetalias{GomesJunior2015} are reduced with the STE ephemeris. \label{Fig: JPL-STE}}
\end{figure}

@@

\begin{table*}
\caption{\label{Tab:STE-error} Mean offsets and standard deviation of the \protect\citetalias{GomesJunior2015} positions relative to the STE, \protect\cite{Jacobson2012} and \protect\cite{Emelyanov2008} ephemeris .}
\begin{centering}
\begin{tabular}{l|cc|cc|cc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
 & \multicolumn{2}{|c|}{STE} & \multicolumn{2}{|c|}{JPL} & \multicolumn{2}{|c}{Eme2008}\tabularnewline
Satellite  & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) \tabularnewline
\hline
Ananke & $-10\pm90$ & $3\pm73$ & $60\pm127$ & $-108\pm99$ & $101\pm180$ & $-107\pm120$ \tabularnewline
Carme & $14\pm73$ & $-1\pm51$ & $-3\pm114$ & $-80\pm102$ & $-6\pm108$ & $-45\pm80$ \tabularnewline
Elara & $3\pm92$ & $-12\pm57$ & $20\pm92$ & $-50\pm69$ & $23\pm94$ & $-83\pm81$ \tabularnewline
Himalia & $-15\pm66$ & $-7\pm54$  & $-19\pm80$  & $-11\pm52$ & $-18\pm72$  & $-13\pm53$ \tabularnewline
Leda & $-9\pm67$ & $-8\pm77$ & $60\pm117$ & $-13\pm95$ & $166\pm162$ & $92\pm95$ \tabularnewline
Lysithea & $15\pm79$ & $-21\pm68$ & $40\pm92$ & $-43\pm77$ & $117\pm193$ & $-76\pm185$ \tabularnewline
Pasiphae & $4\pm89$ & $-16\pm57$ & $-17\pm130$ & $-82\pm85$ & $-10\pm102$ & $-54\pm74$ \tabularnewline
Sinope & $9\pm79$ & $-4\pm47$ & $10\pm228$ & $-35\pm76$ & $11\pm227$ & $-52\pm63$ \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table*}

@@

For the irregular satellites of Jupiter (Ananke, Carme, Elara, Himalia, Leda, Lysithea, Pasiphae and Sinope), we produced ephemeris using only the observations of \citetalias{GomesJunior2015}. The systematic errors found in the JPL ephemeris \citep{Jacobson2012} and \cite{Emelyanov2008} were improved. These new ephemerides are denominated Special-Tailored Ephemeris.

@@

ARG-J thanks the financial support of CAPES.
MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013).
RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj/PAPDRJ-45/2013.
JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6).
BEM thanks the financial support of CAPES.
FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014.
The numerical model of the satellites of Jupiter was developped during a post-doctoral contract funded by the Chinese Academy of Sciences (CAS) and supported by the National Scientific Fund of China (NSFC)

>>>>

\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites for the predictions of stellar occultations up to 2020}
%\title[Orbits and predictions for occultations up to 2020]{New orbits of irregular satellites based on thousands of new observations and predictions for stellar occultations up to 2020}
\author[A. R. Gomes-J\'unior, M. Assafin, L. Beauvalet et al.]{A. R. Gomes-J\'unior$^{1}$\thanks{E-mail: altair08@astro.ufrj.br},
M. Assafin$^{1,\dag}$,
L. Beauvalet$^{2,3}$,
J. Desmars$^{4}$,\newauthor
R. Vieira-Martins$^{1,2,5,\dag}$,
J. I. B. Camargo$^{2,5}$,
B. E. Morgado$^{1,2}$
F. Braga-Ribas$^{2,6}$
\\
$^{1}$Observat\'orio do Valongo/UFRJ, Ladeira Pedro Ant\^onio 43,
CEP 20.080-090 Rio de Janeiro - RJ, Brazil\\
$^{2}$Observat\'orio Nacional/MCTI, R. General Jos\'e Cristino 77, CEP 20921-400 Rio de Janeiro - RJ, Brazil\\
$^{3}$Observatoire de Paris/SYRTE, 77 Avenue Denfert Rochereau 75014 Paris, France\\
$^{4}$Institut de m\'ecanique c\'eleste et de calcul des \'eph\'em\'erides - Observatoire de Paris, UMR 8028 du CNRS, 77 Av. Denfert-Rochereau,\\ 75014 Paris, France\\
$^{5}$Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ 20921-400, Brazil\\
$^{6}$Federal University of Technology - Paran\'a (UTFPR / DAFIS), Rua Sete de Setembro, 3165, CEP 80230-901, Curitiba, PR, Brazil
}
\begin{document}
\newcommand{\noccs}{5442 } % total number of occultations
\defcitealias{GomesJunior2015}{GJ15}

@@

\begin{abstract}
%Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size, shape, albedo and composition, to trace back their true origin. The best ground-based technique to determine size and shape, and thus constrain the albedo and in a broader sense composition, is the observation of stellar occultations by these objects but this demands a very precise ephemeris based on new and good positions.
%\cite{GomesJunior2015} published 6523 observations obtained between 1992 and 2014 for 18 irregular satellites with an estimated error in the positions of about 60 to 80 mas.
%Based on this observations, we aimed to generate new numerical integration of the orbits of eight largest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda. This is a short-time ephemeris that corrected systematic errors from previous ephemeris (JPL JUP300). For Phoebe we updated ephemeris from \cite{Desmars2013} using 75\% more positions than the previous one.
%Also Jupiter will cross the galactic plane in 2019-2020 and Saturn in 2018. This creates a good opportunity to predict stellar occultations due to the large number of events that can be predicted in these periods. Thus, we aimed to predict stellar occultations for the same 9 satellites cited above. Using the UCAC4 catalogue we managed to identify \noccs candidates of stellar occultations between the period of January, 2016 and December, 2020.
%We discuss how the successful observation of a stellar occultation by these objects is quite possible and present some of those potential occultations.
\cite{GomesJunior2015} published \textbf{3613 positions for the 8 largest irregular satellites of Jupiter and 1787 positions for the largest irregular satellite of Saturn, Phoebe}.  These observations were made between \textbf{1995} and 2014 and have an estimated error of about 60 to 80 mas. Based on this set of positions, we performed numerical integrations for deriving new orbits for the eight largest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda. %This corrected systematic errors and resulted in an ephemeris more accurate/precise than JPL jup300 for these bodies at least in the immediate future.
For Phoebe we updated the ephemeris from \cite{Desmars2013} using 75\% more positions than the previous one. Due to their orbital characteristics, it is common belief that the irregular satellites were captured by the giant planets in the early Solar System, but there is no consensus for a single model explaining where they were formed. Size, shape, albedo and composition would help to trace back their true origin, but these physical parameters are yet poorly known for irregular satellites. The observation of stellar occultations would allow for the determination of such parameters. Indeed Jupiter will cross the galactic plane in 2019-2020 and Saturn in 2018, improving a lot the chances of observing such events in the near future. Using the derived ephemerides and the UCAC4 catalogue we managed to identify \noccs candidate stellar occultations between January 2016 and December 2020 for the 9 satellites studied here. We discussed how the successful observation of a stellar occultation by these objects is possible and present some potential occultations.
\end{abstract}

@@

\citetalias{GomesJunior2015} published \textbf{3613} precise positions for \textbf{the 8 largest irregular satellites of Jupiter} from observations made at the Observatório do Pico dos Dias (OPD), Observatoire Haute-Provence (OHP) and European Southern Observatory (ESO) between \textbf{1995} and 2014.

@@

The obtained ephemeris is hereafter refered as STE, for Special-Tailored Ephemeris. The initial osculating elements at the origin of integration, \textbf{the number of observations used and the time-span where these observations are distributed} are presented in Table \ref{Tab: sat_ell}.

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0 with respect to the center of Jupiter.
 }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{lcccccccc}
\hline\hline
Satellite & N & Time-span & a (km) & e & I$\degr$ & $\Omega\degr$ & $\omega\degr$ & $v\degr$ \\ 
\hline
Himalia & 1234 & 1995-2014 &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara & 636 & 1996-2014 &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Lysithea & 234 & 1996-2010 &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Leda & 98 & 1996-2009 &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Pasiphae & 609 & 1996-2013 &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope & 221 & 1996-2009 &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Carme & 331 & 1996-2013 &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke & 250 & 1996-2010 &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular} 
\end{center}
\begin{flushleft}
\textbf{Notes}: N: number of observations used; a: semimajor axis; e : excentricity; I: inclination relative to the equatorial reference plane J2000; $\Omega$: longitude of the ascending node; $\omega$: argument of periapsis; $v$: true anomaly.
\end{flushleft}
\end{table*}

@@

Fig. \ref{Fig: JPL-STE} displays the offsets of the positions published by \citetalias{GomesJunior2015} for the satellite Carme in declination relative to the STE ephemeris, to \cite{Jacobson2012} jup300 JPL ephemeris and \cite{Emelyanov2005}\footnote{\textbf{Last update: February 19, 2012}} ephemeris. \textbf{The DE431 planetary ephemeris \citep{Folkner2014} was used to calculate the positions of Jupiter for the 3 models}. We see that the systematic JPL ephemeris offsets pointed out by \citetalias{GomesJunior2015} are reduced with our ephemeris, as expected.

\begin{figure}
\includegraphics[width=8.8cm]{figures/Carme_ephemeris.eps}
\caption{Offsets in declination of the positions published by \protect\citetalias{GomesJunior2015} for Carme. The red "x" relative to the special-tailored ephemeris, the blue "+" relative to the jup300 JPL ephemeris and the green dot relative to \protect\cite{Emelyanov2005}. As expected, the ephemeris systematic errors pointed out by \protect\citetalias{GomesJunior2015} are reduced with the STE ephemeris. \label{Fig: JPL-STE}}
\end{figure}

@@

\begin{table*}
\caption{\label{Tab:STE-error} Mean offsets and standard deviation of the \protect\citetalias{GomesJunior2015} positions relative to the STE, \protect\cite{Jacobson2012} and \protect\cite{Emelyanov2005} ephemeris .}
\begin{centering}
\begin{tabular}{l|cc|cc|cc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
 & \multicolumn{2}{|c|}{STE} & \multicolumn{2}{|c|}{JPL} & \multicolumn{2}{|c}{Eme2008}\tabularnewline
Satellite  & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) & $\Delta\alpha\cos\delta$ (mas) & $\Delta\delta$ (mas) \tabularnewline
\hline
Himalia & $-15\pm66$ & $-7\pm54$  & $-19\pm80$  & $-11\pm52$ & $-18\pm72$  & $-13\pm53$ \tabularnewline
Elara & $3\pm92$ & $-12\pm57$ & $20\pm92$ & $-50\pm69$ & $23\pm94$ & $-83\pm81$ \tabularnewline
Lysithea & $15\pm79$ & $-21\pm68$ & $40\pm92$ & $-43\pm77$ & $117\pm193$ & $-76\pm185$ \tabularnewline
Leda & $-9\pm67$ & $-8\pm77$ & $60\pm117$ & $-13\pm95$ & $166\pm162$ & $92\pm95$ \tabularnewline
Pasiphae & $4\pm89$ & $-16\pm57$ & $-17\pm130$ & $-82\pm85$ & $-10\pm102$ & $-54\pm74$ \tabularnewline
Sinope & $9\pm79$ & $-4\pm47$ & $10\pm228$ & $-35\pm76$ & $11\pm227$ & $-52\pm63$ \tabularnewline
Carme & $14\pm73$ & $-1\pm51$ & $-3\pm114$ & $-80\pm102$ & $-6\pm108$ & $-45\pm80$ \tabularnewline
Ananke & $-10\pm90$ & $3\pm73$ & $60\pm127$ & $-108\pm99$ & $101\pm180$ & $-107\pm120$ \tabularnewline
\hline
\end{tabular}
\par \end{centering}
\end{table*}

@@

For the irregular satellites of Jupiter (Ananke, Carme, Elara, Himalia, Leda, Lysithea, Pasiphae and Sinope), we produced ephemeris using only the observations of \citetalias{GomesJunior2015}. The systematic errors found in the JPL ephemeris \citep{Jacobson2012} and \cite{Emelyanov2005} were improved. These new ephemerides are denominated Special-Tailored Ephemeris.

@@

ARG-J thanks the financial support of CAPES.
MA thanks the CNPq (Grants 473002/2013-2 and 308721/2011-0) and FAPERJ (Grant E-26/111.488/2013).
RV-M thanks grants: CNPq-306885/2013, Capes/Cofecub-2506/2015, Faperj/PAPDRJ-45/2013.
JIBC acknowledges CNPq for a PQ2 fellowship (process number 308489/2013-6).
BEM thanks the financial support of CAPES.
FB-R acknowledges PAPDRJ-FAPERJ/CAPES E-43/2013 number 144997, E-26/101.375/2014.
The numerical model of the satellites of Jupiter was developped during a post-doctoral contract funded by the Chinese Academy of Sciences (CAS) and supported by the National Scientific Fund of China (NSFC).
